### 2018-12-01 compact_encoding/doc/alt-encoding.tex
Fix bug in doc for alt encoding

\medskip\noindent
The clauses needed for the $F^k_t$ variables establish that no dummy
or inexistent feature is selected, and enforce the strict ordering
among features. The first group corresponds to the following clauses
where $d$ is an index of a dummy or inexistent feature:
\begin{alignat}{1}
  &\bigvee_{t:bit(t,d)} \neg F^k_t \ \lor \bigvee_{t:\neg bit(t,d)} F^k_t
\end{alignat}
where $bit(t,d)$ is a boolean constant for the $t$-th bit in the binary
expansion of $d$.  The ordering among selected featues is enforced with
\begin{alignat}{1}
  &df(k,0) \lor df(k,1) \lor \cdots \lor df(k,L)
\end{alignat}
for $k\in\{0,\ldots,K-2\}$ and $L=\log_2(F)$, and the boolean
variables $df(k,t)$ satisfy
\begin{alignat}{1}
  &df(k,t) \rightarrow \neg F^k_t \,, \\
  &df(k,t) \rightarrow \neg F^{k+1}_t \,, \\
  &df(k,t) \land F^k_i \rightarrow F^{k+1}_i \qquad \text{for $i\in\{t+1,\ldots,L-1\}$} \,, \\
  &df(k,t) \land \neg F^{k+1}_i \rightarrow F^k_i \qquad \text{for $i\in\{t+1,\ldots,L-1\}$} \,.
\end{alignat}
The total number of clauses in (7)--(12) is $K(D+U) + (K-1)(1 + 2L + L(L-1))$
where $D$ and $U$ are the number of dummy and inexistent features respectively.
The total number of clauses in (2)--(12) is
$Q(L,K,N)=N(1+4K) + K(D+U) + (K-1)(L^2 + L) - 1$.

>>>>

\medskip\noindent
The clauses needed for the $F^k_t$ variables establish that no dummy
or inexistent feature is selected, and enforce the strict ordering
among features. The first group corresponds to the following clauses
where $d$ is an index of a dummy or inexistent feature:
\begin{alignat}{1}
  &\bigvee_{t:bit(t,d)} \neg F^k_t \ \lor \bigvee_{t:\neg bit(t,d)} F^k_t
\end{alignat}
where $bit(t,d)$ is a boolean constant for the $t$-th bit in the binary
expansion of $d$.  The ordering among selected featues is enforced with
\begin{alignat}{1}
  &df(k,0) \lor df(k,1) \lor \cdots \lor df(k,L)
\end{alignat}
for $k\in\{0,\ldots,K-2\}$ and $L=\log_2(F)$, and the boolean
variables $df(k,t)$ satisfy
\begin{alignat}{1}
  &df(k,t) \rightarrow \neg F^k_t \,, \\
  &df(k,t) \rightarrow \neg F^{k+1}_t \,, \\
  &df(k,t) \land F^k_i \rightarrow F^{k+1}_i \qquad \text{for $i\in\{t+1,\ldots,L-1\}$} \,, \\
  &df(k,t) \land \neg F^k_i \rightarrow \neg F^{k+1}_i \qquad \text{for $i\in\{t+1,\ldots,L-1\}$} \,.
\end{alignat}
The total number of clauses in (7)--(12) is $K(D+U) + (K-1)(1 + 2L + L(L-1))$
where $D$ and $U$ are the number of dummy and inexistent features respectively.
The total number of clauses in (2)--(12) is
$Q(L,K,N)=N(1+4K) + K(D+U) + (K-1)(L^2 + L) - 1$.
